Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-07 manuscript.Rmd
normative and distinctive accuracy

# Results {.tabset .tabset-fade}

@@

null_models %>% 
  kable_style(title = "<center><b>Null Models</b></center>") %>% 
  kableExtra::pack_rows("Personality", 1, 5) %>% 
  kableExtra::pack_rows("Affect", 6, 10) %>% 
  kableExtra::pack_rows("Thought", 11, 15)

@@

sjPlot::tab_model(null_models2[[1]],
                  null_models2[[2]],
                  null_models2[[3]], 
                  dv.labels = c("Personality", "Affect", "Thought"))

@@

In order to decompose the variance in interpersonal accuracy and compare across accuracy measures I ran a series of baseline variance decomposition models on the accuracy measures. All analyses were conducted in R’s lme4 package (Bates et al., 2013).

```{r}
# personality
## final model
SAM1 <- lmer(ptrait ~ targSRrC + AvgtraitC + 
                (1 | PerUn) + 
                (1 | TarUn) + 
                (1 | DyUn), 
              data = samdata)

sjPlot::tab_model(SAM1)

## extract empirical bayesian estimates for targets
EBTRTtar <- ranef(SAM1)$TarUn
EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
map_dbl(EBTRTtar, sd)

## extract empirical bayesian estimates for perceivers
EBTRTper <- ranef(SAM1)$PerUn
EBTRTper$PerUn<-as.numeric(row.names(EBTRTper))
map_dbl(EBTRTper,sd)

## Density plots for random effects will be placed here

## fit a model for each perceiver
models_dyad <-
samdata %>%
  group_by(PerUn) %>%
  nest() %>%
  mutate(models = map(data, ~ {

    lm(ptrait ~ targSRrC + AvgtraitC,
              data = .x)

  }
                      )
         )
```

```{r}
# affect
samEAC <- lmer (Part ~ targSRrC + NormC + 
                  (targSRrC + NormC|PerUn) + 
                  (targSRrC + NormC|TarUn) + 
                  (targSRrC + NormC|DyUn), 
                data = samEACaggdata)

sjPlot::tab_model(samEAC)

@@

```{r}
# thought
# baseline accuracy
normEASRM<- lmer(BaselineEA100 ~ 
                   (1|PerUn) + 
                   (1|TarUn) + 
                   (1|DyUn) + 
                   (1|Group), 
                 data = eaSRMdata)

# corrected for baseline
diffEASRM<- lmer(CrrctdEAnoneg ~ 
                    (1|PerUn) + 
                    (1|TarUn) + 
                    (1|DyUn) + 
                    (1|Group), 
                  data = eaSRMdata)

sjPlot::tab_model(normEASRM, diffEASRM)
```

## Predictors of interpersonal accuracy

WILL WORK ON THIS LATER.

```{r}

@@

# Discussion

>>>>

# Results and Discussion {.tabset .tabset-fade}

@@

null_models %>% 
  kable_style(title = "<center><b>Table 2. Null Models</b></center>") %>% 
  kableExtra::pack_rows("Personality", 1, 5) %>% 
  kableExtra::pack_rows("Affect", 6, 10) %>% 
  kableExtra::pack_rows("Thought", 11, 15)

@@

@@

All analyses were conducted in R’s lme4 package (Bates et al., 2013). The

```{r}
# for looping purposes
df_personality_self <- 
  df_personality %>% 
  select(perceiver_id:judgment,
         norm = self_norm,
         distinct = self_dist)

df_personality_inf <- 
  df_personality %>% 
  select(perceiver_id:judgment,
         norm = inf_norm,
         distinct = inf_dist)

df_affect <- 
  df_affect %>% 
  rename(distinct = self_dist)

df_list2 <- list(df_personality_self,
                 df_personality_inf,
                 df_affect)

# models
models_norm_distinct <- 
  map_dfr(df_list2, ~

            lmer(judgment ~ distinct + norm +
                   (1|perceiver_id) + 
                   (1|target_id) +
                   (1|dyad_id),
                 data = .x) %>%

        broom.mixed::tidy()
          )

# Accuracy for thoughts is a little different. So, we'll only have two null models for distinctive and normative accuracy for thoughts. See the methods section for details.

models_norm_distinct_thoughts <- 
  df_thought %>% 
  rename(Normative = BaselineEA100,
         Distinctive = CrrctdEAnoneg) %>% 
  pivot_longer(cols = c(Normative, Distinctive),
               names_to = "DVs",
               values_to = "rating") %>% 
  split(., .$DVs) %>% 
  map(., ~

        lmer(rating ~ 
               (1|perceiver_id) + 
               (1|target_id) +
               (1|dyad_id),
             data = .x)

        )

map_dfr(models_norm_distinct_thoughts, isSingular) %>% 
  kable_style(title = "<center><b>Are the models for thought accuracy singular?</b></center>")

model_norm_thought <- lmer(BaselineEA100 ~ 
                             (1|perceiver_id),
                           data = df_thought) %>% broom.mixed::tidy()

model_dist_thought <- lmer(CrrctdEAnoneg ~ 
                             (1|perceiver_id) + 
                             (1|target_id) +
                             (1|dyad_id),
                           data = df_thought) %>% broom.mixed::tidy()

@@

Since the model for normative thought accuracy is singular, we ran the models separately.

```{r}
bind_rows(models_norm_distinct,
          model_norm_thought,
          model_dist_thought) %>% 
  kable_style(title = "<center><b>Table 3. Normative and Distinctive Accuracy</b></center>") %>% 
  kableExtra::pack_rows("Self-reported Personality", 1, 7) %>% 
  kableExtra::pack_rows("Informant-reported Personality", 8, 14) %>% 
  kableExtra::pack_rows("Affect", 15, 21) %>% 
  kableExtra::pack_rows("Normative Thought", 22, 24) %>% 
  kableExtra::pack_rows("Distinctive Thought", 25, 29)
```

## Predictors of interpersonal accuracy
The last aim of the present study is to test individual-difference predictors of interpersonal accuracy. Table 3 demonstrates the relationship between the predictors and interpersonal accuracy across domains.

```{r}
df_thought_long <- 
  df_thought %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value")

df_thought_long <- split(df_thought2, df_thought2$vars)

models5 <- map_dfr(df_thought5, ~
            lmer(judgment ~ value +
             (1 | perceiver_id) + 
             (1 | target_id) +
             (1 | dyad_id),
           data = .x) %>% 
             broom.mixed::tidy() %>% 
             suppressWarnings(), 
           .id = "Predictors"
           )

df_thought5 <- 
  df_thought5 %>% 
  mutate(m1 = map(data, ~
            lmer(judgment ~ value +
             (1 | perceiver_id) + 
             (1 | target_id) +
             (1 | dyad_id),
           data = .x)
                 )
         )

df_thought3 <- 
  df_thought %>% 
  pivot_longer(cols = InsecAtt_c:rapport_c,
               names_to = "vars",
               values_to = "value") %>% 
  group_by(vars) %>% 
  nest()

df_thought3 <- 
  df_thought3 %>% 
  mutate(m1 = map(data, ~
            lmer(judgment ~ value +
             (1 | perceiver_id) + 
             (1 | target_id) +
             (1 | dyad_id),
           data = .x)
                 )
         )

@@
